---
title: "drak_ct"
author: "Tatini Mal-Sarkar"
date: "12/24/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lavaan)
library(semPlot)
library(ggridges)
library(dplyr)
library(aod)
```

# Loading the data
```{r drak_load}
drak = read_csv("/Users/tatinimal-sarkar/Documents/mph2/practicum/thesis/data/KerryDataRequestV2_visit1_c.csv") %>% 
  select(-ASSIST_Tobacco_Score:-opioids_preg_any,
         -AQ1a:-AQ14b,
         -pdiq1_afr:-pdiq13_xho,
         -leq1_1_afr:-leq51_2_xho,
         -ipvq1_afr:-ipvq17_xho,
         -epdsq1_afr:-epdsq10_xho,
         -bdiq1_afr:-bdiq25_2_xho,
         -srqq1_afr:-srqq20_xho) %>% 
  mutate(ethnicity = as.numeric(ethnicity > 1),
         clinic = as.numeric(Clinic > 1),
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1,
         revsum9 = 5 - sumses9) %>% 
  filter(SESaQ31_1 != 6,
         SESaQ34_1 != 4) %>% 
  mutate(housing = as.numeric(SESaQ31_1 > 2),
         owner = as.numeric(SESaQ34_1 == 1),
         ses = revsum9 + housing + owner + sumses33) %>% 
  select(-Clinic) %>% 
  mutate(kids = 5 - SESaQ1,
         people = 20 - SESaQ2,
         adults = 3 - SESaQ3_1,
         school = SESaQ14 - 2,
         job = 6 - SESaQ15_1,
         aid = 1 - SESaQ16,
         ownincome = SESaQ18,
         houseincome = SESaQ19
         ) %>%
  filter(
         job != -3,
         ownincome != 99,
         ownincome != 9999,
         houseincome != 99,
         houseincome != 9999) %>% 
  mutate(ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome,
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1)
```

# Socioeconomic status and depression
```{r drak_nomed}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome 
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ ses '

fit <- sem(model, data = drak, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# Socioeconomic status, depression, and 1-factor childhood trauma
```{r drak_med}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23 

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak, missing = 'fiml.x', group = "clinic")
summary(fit)

semPaths(fit, title = FALSE, curvePivot = TRUE)
```

# Socioeconomic status, depression, and 2-factor childhood trauma
```{r drak_med_2}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf1 =~ ctq3 + ctq4 + ctq8 + ctq9 + ctq11 + ctq12 + ctq14 + ctq15 + ctq17 + ctq18+ ctq25 
trauf2 =~ ctq20 + ctq21 + ctq23 + ctq24 + ctq27

depf1 ~ c*trauf1 + d*trauf2 + e*ses
trauf1 ~ a*ses 
trauf2 ~ b*ses

indirect := a*c + b*d
total := e + (a*c + b*d)
'

fit <- sem(model, drak, missing = 'fiml.x', group = "clinic")
summary(fit)
```


# Plot of CTQ by SES category
```{r drak_plot}
drak_plot = drak %>% 
  mutate(ctq = ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23,
         ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome,
         ses1 = ses <= 5,
         ses2 = ses > 5 & ses <= 10,
         ses3 = ses > 10 & ses <= 15,
         ses4 = ses > 15 & ses <= 20,
         ses5 = ses > 20 & ses <= 25,
         ses6 = ses > 25) %>%
  gather(ses1:ses6, key = "sescat", value = "bin") %>% 
  filter(bin == TRUE) %>% 
  select(-bin) %>% 
  group_by(sescat) %>% 
  summarize(mean_ctq = mean(ctq, na.rm = TRUE),
            sd_ctq = sd(ctq, na.rm = TRUE)) %>% 
  ungroup() %>% 
  ggplot(aes(x = sescat, y = mean_ctq)) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_ctq - sd_ctq, ymax = mean_ctq + sd_ctq), width = 0.2) +
  labs(x = "Category of socioeconomic status",
       y = "Childhood trauma")

```

# Plot with extended CTQ
```{r}
drakplot2 = drak %>% 
  mutate(ctq2rev = 6 - ctq2,
         ctq5rev = 6 - ctq5,
         ctq7rev = 6 - ctq7,
         ctq10rev = 6 - ctq10,
         ctq13rev = 6 - ctq13,
         ctq16rev = 6 - ctq16,
         ctq19rev = 6 - ctq19,
         ctq22rev = 6 - ctq22,
         ctq26rev = 6 - ctq26,
         ctq28rev = 6 - ctq28,
         ctq = ctq1 + ctq2rev + ctq3 + ctq4 + ctq5rev + ctq6 + ctq7rev + ctq8 + ctq9 + ctq10rev + ctq11 + ctq12 + ctq13rev + ctq14 + ctq15 + ctq16rev + ctq17 + ctq18 + ctq19rev + ctq20 + ctq21 + ctq22rev + ctq23 + ctq24 + ctq25 + ctq26rev + ctq27 + ctq28rev,
         ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome,
         ses1 = ses <= 5,
         ses2 = ses > 5 & ses <= 10,
         ses3 = ses > 10 & ses <= 15,
         ses4 = ses > 15 & ses <= 20,
         ses5 = ses > 20 & ses <= 25,
         ses6 = ses > 25) %>%
  gather(ses1:ses6, key = "sescat", value = "bin") %>% 
  filter(bin == TRUE) %>% 
  select(-bin) %>% 
  group_by(sescat) %>% 
  summarize(mean_ctq = mean(ctq, na.rm = TRUE),
            sd_ctq = sd(ctq, na.rm = TRUE)) %>% 
  ungroup() %>% 
  ggplot(aes(x = sescat, y = mean_ctq)) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_ctq - sd_ctq, ymax = mean_ctq + sd_ctq), width = 0.2) +
  labs(x = "Category of socioeconomic status",
       y = "Childhood trauma") 
```


# Socioeconomic status and 2-factor childhood trauma
```{r drak_sesctq}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
trauf1 =~ ctq3 + ctq4 + ctq8 + ctq9 + ctq11 + ctq12 + ctq14 + ctq15 + ctq17 + ctq18+ ctq25 
trauf2 =~ ctq20 + ctq21 + ctq23 + ctq24 + ctq27 

trauf1 ~ ses
trauf2 ~ ses'

fit <- sem(model, drak, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# Socioeconomic status and 1-factor childhood trauma
```{r drak_sesctq2}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
trauf =~ ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23 

trauf ~ ses '

fit <- sem(model, drak, missing = 'fiml.x', group = "clinic")
summary(fit)
```


# Cleaning dataset for logistic regressions
```{r}
drak_log = drak %>% 
  mutate(bdiq16 = as.numeric(str_sub(bdiq16, 0, 1)),
         bdiq18 = as.numeric(str_sub(bdiq18, 0, 1)),
         bdi = bdiq1 + bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq9 + bdiq10 + bdiq11 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq16 + bdiq17 + bdiq18 + bdiq19 + bdiq20 + bdiq21,
         mild_dep = bdi > 13 & bdi < 20,
         mod_dep = bdi > 19 & bdi < 29,
         sev_dep = bdi > 28,
         all_dep = bdi > 13,
         ctq2rev = 6 - ctq2,
         ctq5rev = 6 - ctq5,
         ctq7rev = 6 - ctq7,
         ctq10rev = 6 - ctq10,
         ctq13rev = 6 - ctq13,
         ctq16rev = 6 - ctq16,
         ctq19rev = 6 - ctq19,
         ctq22rev = 6 - ctq22,
         ctq26rev = 6 - ctq26,
         ctq28rev = 6 - ctq28,
         ctq = ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23,
         ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome)
```

# Logistic regression of severe depression on childhood trauma, adjusted for age and clinic
```{r}
mylogit = glm(sev_dep ~ ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of severe depression on SES, adjusted for age and clinic
```{r}
mylogit = glm(sev_dep ~ ses + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of severe depression on SES, adjusted for CTQ, age, and clinic
```{r}
mylogit = glm(sev_dep ~ ses + ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of moderate depression on SES, adjusted for age and clinic
```{r}
mylogit = glm(mod_dep ~ ses + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of moderate depression on SES, adjusted for CTQ, age, and clinic
```{r}
mylogit = glm(mod_dep ~ ses + ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of mild depression on SES, adjusted for age and clinic
```{r}
mylogit = glm(mild_dep ~ ses + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of mild depression on SES, adjusted for CTQ, age, and clinic
```{r}
mylogit = glm(mild_dep ~ ses + ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of all depression on SES, adjusted for age and clinic
```{r}
mylogit = glm(all_dep ~ ses + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of all depression on SES, adjusted for CTQ, age, and clinic
```{r}
mylogit = glm(all_dep ~ ses + ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of all depression on CTQ, adjusted for age and clinic
```{r}
mylogit = glm(all_dep ~ ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of mild depression on CTQ, adjusted for age and clinic
```{r}
mylogit = glm(mild_dep ~ ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of moderate depression on CTQ, adjusted for age and clinic
```{r}
mylogit = glm(mod_dep ~ ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# Logistic regression of severe depression on CTQ, adjusted for age and clinic
```{r}
mylogit = glm(sev_dep ~ ctq + mother_age_at_enrolment + clinic, data = drak_log, family = "binomial")

summary(mylogit)

confint(mylogit)

exp(coef(mylogit))

exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

# 1-factor childhood trauma and SES
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
trauf =~ ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23 

ses ~ trauf
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# SES and depression
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ ses
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# Socioeconomic status, 1-factor childhood trauma, and depression
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23 

depf1 ~ a*trauf + b*ses
ses ~ c*trauf

indirect := b*c
total := a + (b*c)
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# Socioeconomic status, physical neglect, and depression
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
physneg =~ ctq2rev + ctq26rev + ctq6 + ctq1 + ctq4

depf1 ~ a*physneg + b*ses
ses ~ c*physneg

indirect := b*c
total := a + (b*c)
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# SES and depression
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ MPSSQ1 + MPSSQ2 + MPSSQ3 + MPSSQ4 + MPSSQ5 + MPSSQ6 + MPSSQ7 + MPSSQ8 + MPSSQ9 + MPSSQ10 + MPSSQ11 + MPSSQ12 + MPSSQ13 + MPSSQ14 + MPSSQ15 + MPSSQ16 + MPSSQ17 + MPSSQ18 

depf1 ~ ses
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```

# Socioeconomic status, PTSD, and depression
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ MPSSQ1 + MPSSQ2 + MPSSQ3 + MPSSQ4 + MPSSQ5 + MPSSQ6 + MPSSQ7 + MPSSQ8 + MPSSQ9 + MPSSQ10 + MPSSQ11 + MPSSQ12 + MPSSQ13 + MPSSQ14 + MPSSQ15 + MPSSQ16 + MPSSQ17 + MPSSQ18 

depf1 ~ a*ses + b*trauf
trauf ~ c*ses

indirect := b*c
total := a + (b*c)
'

fit <- sem(model, drak_log, missing = 'fiml.x', group = "clinic")
summary(fit)
```