---
title: "prelim drak"
author: "Tatini Mal-Sarkar"
date: "11/14/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lavaan)
library(semPlot)
library(ggridges)
library(dplyr)
```

```{r drak_load}
drak = read_csv("/Users/tatinimal-sarkar/Documents/mph2/practicum/thesis/data/KerryDataRequestV2_visit1_c.csv") %>% 
  select(-ASSIST_Tobacco_Score:-opioids_preg_any,
         -AQ1a:-AQ14b,
         -pdiq1_afr:-pdiq13_xho,
         -leq1_1_afr:-leq51_2_xho,
         -ipvq1_afr:-ipvq17_xho,
         -epdsq1_afr:-epdsq10_xho,
         -bdiq1_afr:-bdiq25_2_xho,
         -srqq1_afr:-srqq20_xho)
```

# Model 1
## No mediator
```{r drak_sem_nomed_1}
nomed_mod <- 'pov =~ SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + SESaQ32 + SESaQ34_1 + sumses9 + sumses33
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov
depf2 ~ pov '

nomed_mod_fit_1 <- sem(nomed_mod, data = drak, missing = 'fiml.x')
summary(nomed_mod_fit_1)
```

## With mediator
```{r drak_sem_med_1}
med_mod <- 'pov =~ SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + SESaQ32 + SESaQ34_1 + sumses9 + sumses33
trauf1 =~ MPSSQ2 + MPSSQ3 + MPSSQ4 + MPSSQ5 + MPSSQ6 + MPSSQ7 + MPSSQ8 + MPSSQ9 + MPSSQ10 + MPSSQ11 + MPSSQ12 + MPSSQ13 + MPSSQ14 + MPSSQ15 + MPSSQ16 + MPSSQ17 + MPSSQ18
trauf2 =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ trauf1 + trauf2 + pov
depf2 ~ trauf1 + trauf2 + pov
trauf1 ~ pov
trauf2 ~ pov '

med_mod_fit_1 <- sem(med_mod, data = drak, missing = 'fiml.x')
summary(med_mod_fit_1)
```

# Model 2
This model excludes PTSD from trauma.

## No mediator
```{r drak_sem_nomed_2}
nomed_mod <- 'pov =~ SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + SESaQ32 + SESaQ34_1 + sumses9 + sumses33
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov
depf2 ~ pov '

nomed_mod_fit_2 <- sem(nomed_mod, data = drak, missing = 'fiml.x')
summary(nomed_mod_fit_2)
```

## With mediator
```{r drak_sem_med_2}
med_mod <- 'pov =~ SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + SESaQ32 + SESaQ34_1 + sumses9 + sumses33
trauf2 =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ trauf2 + pov
depf2 ~ trauf2 + pov
trauf2 ~ pov '

med_mod_fit_2 <- sem(med_mod, data = drak, missing = 'fiml.x')
summary(med_mod_fit_2)
```


# Model 3
This model has even fewer variables on poverty than Model 1. Trauma here is only IPV, not PTSD.

## No mediator
```{r drak_sem_nomed_3}
nomed_mod <- 'pov =~ sumses9 + ethnicity + SESaQ31_1 + sumses33 + SESaQ34_1
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov
depf2 ~ pov '

nomed_mod_fit_3 <- sem(nomed_mod, data = drak, missing = 'fiml.x')
summary(nomed_mod_fit_3)
```

## With mediator
```{r drak_sem_med_3}
med_mod <- 'pov =~ sumses9 + ethnicity + SESaQ31_1 + sumses33 + SESaQ34_1
trauf2 =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ trauf2 + pov
depf2 ~ trauf2 + pov
trauf2 ~ pov '

med_mod_fit_3 <- sem(med_mod, data = drak, missing = 'fiml.x')
summary(med_mod_fit_3)
```

# Model 4
This model only uses IPV and extends poverty.

## No mediator

```{r drak_sem_nomed_4}
nomed_mod <- 'pov =~ SESaQ3_1 + sumses9 + SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + sumses33 + SESaQ34_1 + ethnicity
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov
depf2 ~ pov '

nomed_mod_fit_4 <- sem(nomed_mod, data = drak, missing = 'fiml.x')
summary(nomed_mod_fit_4)
```

```{r drak_sem_med_4}
med_mod <- 'pov =~ SESaQ3_1 + sumses9 + SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + sumses33 + SESaQ34_1 + ethnicity
trauf2 =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21
depf2 =~ bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ trauf2 + pov
depf2 ~ trauf2 + pov
trauf2 ~ pov '

med_mod_fit_4 <- sem(med_mod, data = drak, missing = 'fiml.x')
summary(med_mod_fit_4)
```

```{r drak_dep_nomed}
nomed_mod <- 'pov =~ sumses9 + ethnicity + SESaQ31_1 + sumses33 + SESaQ34_1
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov '

nomed_mod_fit <- sem(nomed_mod, data = drak, missing = 'fiml.x')
summary(nomed_mod_fit)
```

```{r drak_dep_med}
med_mod <- 'pov =~ sumses9 + ethnicity + SESaQ31_1 + sumses33 + SESaQ34_1
trauf2 =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ trauf2 + pov
trauf2 ~ pov '

med_mod_fit <- sem(med_mod, data = drak, missing = 'fiml.x')
summary(med_mod_fit)
```

```{r drak_efa}
drak %>% 
  mutate(pov_sum = SESaQ3_1 + sumses9 + SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + sumses33 + SESaQ34_1,
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1) %>% 
  group_by(Clinic) %>% 
  ggplot(aes(x = pov_sum, y = bdi, color = ethnicity)) + 
    geom_point() +
  facet_grid(~ Clinic)
```

```{r drak_lm}
drak_lm = drak %>% 
  mutate(pov_sum = SESaQ3_1 + sumses9 + SESaQ13_1 + SESaQ14 + SESaQ15_1 + SESaQ20_1 + SESaQ21 + SESaQ31_1 + sumses33 + SESaQ34_1,
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1)

fit = lm(bdi ~ pov_sum + ethnicity + Clinic, data = drak_lm) 

fit %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

fit_2 = lm(bdi ~ sumses33, data = drak_lm)

fit_2 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r drak_dep_sumses9}
drak %>% 
  mutate(bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1) %>% 
  group_by(Clinic) %>% 
  ggplot(aes(x = sumses9, y = bdi, color = ethnicity)) + 
    geom_point() +
    geom_smooth() +
  facet_grid(~ Clinic)
```

```{r drak_dep_sumses33}
drak %>% 
  mutate(bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1) %>% 
  group_by(Clinic) %>% 
  ggplot(aes(x = sumses33, y = bdi, color = ethnicity)) + 
    geom_point() +
    geom_smooth() +
  facet_grid(~ Clinic)
```


Recoding ethnicity to 0 (Black) and 1 (Coloured). 
Recoding clinic to 0 (Mbekweni) and 1 (TC Newman).
Recode everything as SES, not poverty (sumses9, SESaQ31_1, sumses33, SESaQ34_1).
Filtered out moms whose housing is "Other"
Recoding housing to 0 (shack, wendy house/backyard dwelling) and 1 (house or flat).
Recoding owner to 0 (informal, rent) and 1 (own).
Hypothesis: increase SES, decrease BDI
```{r drak_clean}
drak_clean = drak %>% 
  mutate(ethnicity = as.numeric(ethnicity > 1),
         clinic = as.numeric(Clinic > 1),
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1,
         revsum9 = 5 - sumses9) %>% 
  filter(SESaQ31_1 != 6,
         SESaQ34_1 != 4) %>% 
  mutate(housing = as.numeric(SESaQ31_1 > 2),
         owner = as.numeric(SESaQ34_1 == 1),
         ses = revsum9 + housing + owner + sumses33) %>% 
  select(-Clinic)
  
  drak_clean %>% 
    group_by(clinic, owner) %>% 
    summarize(n = n()) %>% 
    ggplot(aes(x = owner, y = n, color = clinic)) +
    geom_point()
```

```{r drak_clean_plot}
drak_clean %>% 
  group_by(clinic) %>% 
  ggplot(aes(x = ses, y = bdi, color = ethnicity)) + 
    geom_point() +
    geom_smooth() +
    facet_grid(~ clinic)
```

I want to stratify this by clinic!
```{r drak_clean_nomed}
nomed_mod_cl <- 'ses =~ revsum9 + housing + owner + sumses33 
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ ses '

nomed_mod_fit_cl <- sem(nomed_mod_cl, data = drak_clean, missing = 'fiml.x', group = "clinic")
summary(nomed_mod_fit_cl)
```

Mediation analysis
```{r drak_med}
model <- 'ses =~ revsum9 + housing + ethnicity + owner + sumses33
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_clean, "bootstrap")
summary(fit)
  
```

Tried doing this a different way.
Recoding ethnicity to 0 (Black) and 1 (Coloured). 
Recoding clinic to 0 (Mbekweni) and 1 (TC Newman).
Recode everything as poverty, not SES (sumses9, SESaQ31_1, sumses33, SESaQ34_1).
Filtered out moms whose housing is "Other"
Recoding housing to 1 (shack, wendy house/backyard dwelling) and 0 (house or flat).
Recoding owner to 1 (informal, rent) and 0 (own).
Hypothesis: increase poverty, increase BDI
```{r}
drak_clean_pov = drak %>% 
  mutate(ethnicity = as.numeric(ethnicity > 1),
         clinic = as.numeric(Clinic > 1),
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1,
         revsum33 = 9 - sumses33) %>% 
  filter(SESaQ31_1 != 6,
         SESaQ34_1 != 4) %>% 
  mutate(housing = as.numeric(SESaQ31_1 < 3),
         owner = as.numeric(SESaQ34_1 > 1),
         ses = sumses9 + housing + owner + revsum33) %>% 
  select(-Clinic)
```

```{r}
nomed_mod_cl <- 'pov =~ sumses9 + housing + owner + revsum33 
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ pov '

nomed_mod_fit_cl <- sem(nomed_mod_cl, data = drak_clean_pov, missing = 'fiml.x', group = "clinic")
summary(nomed_mod_fit_cl)
```

Mediation analysis
```{r drak_med}
model <- 'pov =~ sumses9 + housing + owner + revsum33
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15

depf1 ~ b*trauf + c*pov
trauf ~ a*pov

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_clean_pov, "bootstrap")
summary(fit)
  
```

Dummy variables for SES (categorical; reference = 0 <= ses <= 4; 
group 1 = 4 < ses <= 8; 
group 2 = 8 < ses <= 12;
group 3 = 12 < ses <= 16)
```{r drak_clean_cat}
drak_clean_cat = drak_clean %>% 
  mutate(ses1 = ifelse(ses > 4 & ses <= 8, 1, 0),
         ses2 = ifelse(ses > 8 & ses <= 12, 1, 0),
         ses3 = ifelse(ses > 12 & ses <= 16, 1, 0)) 

model <- 'ses =~ ses1 + ses2 + ses3
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_clean_cat, "bootstrap")
summary(fit)
```

Restrict to moms in Mbekweni?
```{r restrict}
drak_blmbek = drak_clean %>% 
  mutate(kids = 5 - SESaQ1,
         people = 20 - SESaQ2,
         adults = 3 - SESaQ3_1,
         school = SESaQ14 - 2,
         job = 6 - SESaQ15_1,
         aid = 1 - SESaQ16,
         ownincome = SESaQ18,
         houseincome = SESaQ19,
         ipvq1 = ipvq1 - 1,
         ipvq2 = ipvq2 - 1,
         ipvq3 = ipvq3 - 1,
         ipvq4 = ipvq4 - 1,
         ipvq5 = ifelse(ipvq5 == 2, 0, ipvq5),
         ipvq6 = ipvq6 - 1,
         ipvq7 = ipvq7 - 1,
         ipvq8 = ipvq8 - 1,
         ipvq9 = ipvq9 - 1,
         ipvq10 = ipvq10 - 1,
         ipvq11 = ifelse(ipvq11 == 2, 0, ipvq11),
         ipvq12 = ipvq12 - 1,
         ipvq13 = ipvq13 - 1,
         ipvq14 = ipvq14 - 1,
         ipvq15 = ifelse(ipvq15 == 2, 0, ipvq15)
         ) %>%
  filter(clinic == 0,
         job != -3,
         ownincome != 99,
         ownincome != 9999,
         houseincome != 99,
         houseincome != 9999) %>% 
  mutate(ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome,
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1)

ggplot(drak_blmbek, aes(x = ses, y = bdi), color = ethnicity) + 
  geom_point() + 
  geom_smooth()
```

```{r drak_blmbek_nomed}
nomed_mod_cl <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome 
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ ses '

nomed_mod_fit_cl <- sem(nomed_mod_cl, data = drak_blmbek, missing = 'fiml.x')
summary(nomed_mod_fit_cl)
```

```{r med}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_blmbek, missing = 'fiml.x')
summary(fit)
```

Stratifying by clinic, but including both
```{r restrict_total}
drak_new = drak_clean %>% 
  mutate(kids = 5 - SESaQ1,
         people = 20 - SESaQ2,
         adults = 3 - SESaQ3_1,
         school = SESaQ14 - 2,
         job = 6 - SESaQ15_1,
         aid = 1 - SESaQ16,
         ownincome = SESaQ18,
         houseincome = SESaQ19,
         ipvq1 = ipvq1 - 1,
         ipvq2 = ipvq2 - 1,
         ipvq3 = ipvq3 - 1,
         ipvq4 = ipvq4 - 1,
         ipvq5 = ifelse(ipvq5 == 2, 0, ipvq5),
         ipvq6 = ipvq6 - 1,
         ipvq7 = ipvq7 - 1,
         ipvq8 = ipvq8 - 1,
         ipvq9 = ipvq9 - 1,
         ipvq10 = ipvq10 - 1,
         ipvq11 = ifelse(ipvq11 == 2, 0, ipvq11),
         ipvq12 = ipvq12 - 1,
         ipvq13 = ipvq13 - 1,
         ipvq14 = ipvq14 - 1,
         ipvq15 = ifelse(ipvq15 == 2, 0, ipvq15)
         ) %>%
  filter(
         job != -3,
         ownincome != 99,
         ownincome != 9999,
         houseincome != 99,
         houseincome != 9999) %>% 
  mutate(ses = housing + owner + sumses33 + school + job + aid + ownincome + houseincome,
         bdi = bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1)
```

No mediator
```{r drak_new_nomed}
nomed_mod_cl <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome 
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1

depf1 ~ ses '

nomed_mod_fit_cl <- sem(nomed_mod_cl, data = drak_new, missing = 'fiml.x', group = "clinic")
summary(nomed_mod_fit_cl)
```

Including mediator
```{r med}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq4 + ipvq5 + ipvq6 + ipvq7 + ipvq8 + ipvq9 + ipvq10 + ipvq11 + ipvq12 + ipvq13 + ipvq14 + ipvq15

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_new, missing = 'fiml.x', group = "clinic")
summary(fit)
```

Try again to get IPV valence correct
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ipvq1 + ipvq2 + ipvq3 + ipvq10 + ipvq12 + ipvq13 + ipvq14

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_new, missing = 'fiml.x', group = "clinic")
summary(fit)
```

Try it with childhood trauma
```{r}
model <- 'ses =~ housing + owner + sumses33 + school + job + aid + ownincome + houseincome
depf1 =~ bdiq2 + bdiq3 + bdiq4 + bdiq5 + bdiq6 + bdiq7 + bdiq8 + bdiq10 + bdiq12 + bdiq13 + bdiq14 + bdiq15 + bdiq17 + bdiq20 + bdiq21 + bdiq22_1 + bdiq23_1 + bdiq24_1 + bdiq25_1
trauf =~ ctq1 + ctq3 + ctq4 + ctq6 + ctq8 + ctq9 + ctq11 + ctq14 + ctq20 + ctq23 

depf1 ~ b*trauf + c*ses
trauf ~ a*ses

indirect := a*b
total := c + (a*b)
'

fit <- sem(model, drak_new, missing = 'fiml.x', group = "clinic")
summary(fit)
```

